Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-08-01 paperIEEE.tex
Tweaks
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@142 db7c848b-7755-4df2-b763-8796797afa52

During data synchronization, the master commits the object data to all mapped
slave instances simultaneously. This is a ``push'' operation, whereas the
mapping is a slave-triggered ``pull'' operation. Furthermore, the buffers only
have to be serialized and compressed once, and then can be sent directly to all
mapped slave nodes. Slave nodes queue this data and consume it during
synchronization. In contrast, object mapping needs to wait for each slave node
to request the mapping, and then may need to reserialize and compress the
object data. We test the time to commit and sync the data using different
compression engines.

The David statue at 2\,mm resolution is organized in a k-d tree for rendering. Each
node is a separate distributed object, which has two child node objects. A
total of $1023$ objects is distributed and synchronized. \fig{fDavidDist} shows
the distribution times for this data set. Due to limited compressibility of the
data, the results are relatively similar. Compressing the data repeatedly for
each client leads to decreased performance, since the compression overhead
cannot be amortized by the decreased transmission time. Buffering data slightly
improves performance by reducing the CPU and copy overhead. Combining
compression and buffering leads to the best performance, although only by about
10\%.

>>>>

During data synchronization, the master commits the object data to all mapped
slave instances simultaneously. This is a ``push'' operation, whereas the
mapping is a slave-triggered ``pull'' operation. During commit, the buffers
only have to be serialized and compressed once, and then can be sent directly
to all mapped slave nodes. Slave nodes queue this data and consume it during
synchronization. In contrast, object mapping needs to wait for each slave node
to request the mapping, and then may need to reserialize and compress the
object data. We test the time to commit and sync the data using different
compression engines.

The David statue at 2\,mm resolution is organized in a k-d tree for rendering. Each
node is a separate distributed object, which has two child node objects. A
total of $1023$ objects are distributed and synchronized. \fig{fDavidDist} shows
the distribution times for this data set. Due to limited compressibility of the
data, the results are relatively similar. Compressing the data repeatedly for
each client leads to decreased performance, since the compression overhead
cannot be amortized by the decreased transmission time. Buffering data slightly
improves performance by reducing the CPU and copy overhead. Combining
compression and buffering leads to the best performance, although only by about
10\%.
